%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}
\vspace{-.3\baselineskip}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {
    {Food Lion}
    {\newline}
    \vspace{-.25\baselineskip}
    {Home Depot}
    \vspace{-.5\baselineskip}
    {\newline}
    {Wal-Mart}
    } % Job title
    {Cashier \vspace{-.4\baselineskip}} % Organization
    {Apex \& Holly Springs, NC, U.S.A \vspace{-.4\baselineskip}} % Location
    {
    {Mar 2018 - Sep 2018}
    {\newline}
    \vspace{-.25\baselineskip}
    {Jul 2016 - Oct 2017}
    \vspace{-.5\baselineskip}
    {\newline}
    {Mar 2015 - Dec 2015}
    }% Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Responsible for taking money in the form of cash, check, or credit card in compliance to store procedures.}
        \item {Scans items, provides change and processes card transactions according to store requirements.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {United States Postal Service
    } % Job title
    {PSE Sales Distribution Associate} % Organization
    {Apex, NC, U.S.A} % Location
    {Nov 2017 - Jan 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Responsible for maintaining sufficient inventory of packages and mail, and distributing them appropriately.}
        \item {Verify and sort bulk mailings and compute and maintain them respectively.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {CVS Pharmacy} % Job title
    {Pharmacy Technician} % Organization
    {Apex, NC, U.S.A} % Location
    {Feb 2013 - Jun 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintains pharmacy inventory by checking pharmaceutical stock, packages medications and supplies, placing and expediting orders, verifying receipt, removing outdated drugs.}
        \item {Organizes medications for pharmacist by reading medication orders and prescriptions, preparing labels, calculating quantities and assembling intravenous solutions.}
      \end{cvitems}
    }

%---------------------------------------------------------
    \cventry
    {K.V. Central Government Schools} % Job title
    {Primary School Teacher} % Organization
    {Punjab, India} % Location
    {Aug 2009 - Feb 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Instructs students individually and in groups, in compliance to various teaching methods such as lectures, discussions, and demonstrations.}
        \item {Sponsors extracurricular activities such as clubs, student organizations, and other academic activities.}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {
    {D.A.V. Public School}
    {\newline}
    \vspace{-.4\baselineskip}
    {Krishna Model High School}
    } % Job title
    {K-12 Teacher | Supervisor} % Organization
    {Punjab \& Himachal Pradesh, India} % Location
    {
    {Apr 2009 – Jul 2009}
    {\newline}
    \vspace{-.4\baselineskip}
    {May 1999 – Jul 2003}
    }% Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Plan, organize and implement an appropriate instructional program in an elementary and secondary learning environment that guides and encourages students to develop and fulfill their academic potential.}
        \item {Responsible for budgets, teaching schedules, supplies, disciplinary actions, teacher and staff evaluations, and communications with the public on behalf of school.}
      \end{cvitems}
    }

%---------------------------------------------------------
    \cventry
    {Krishna Pharmacy Drug Store} % Job title
    {Pharmacy Manager} % Organization
    {Himachal Pradesh, India} % Location
    {Mar 2008 - Apr 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Responsible for production, compounding, and apportioning of medicines in a hospital pharmacy.}
        \item {Dispenses drugs prescribed by physicians and other health practitioners and provides information to patients about medications and their use.}
      \end{cvitems}
    }
%---------------------------------------------------------
    \cventry
    {Goyal Nursing Home} % Job title
    {Nurse Aide} % Organization
    {Himachal Pradesh, India} % Location
    {Feb 1996 - Apr 2003} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Make a plan to restore patients' health by collaborating with nurses, physicians and multidisciplinary team members.}
        \item{Assist with activities of daily living by giving bedpans, urinals, baths, backrubs, shampoos, and shaves.}
      \end{cvitems}
    }
%---------------------------------------------------------

\end{cventries}
